---
title: "AI_in_Course_Syllabi"
subtitle: "extract_text"
author: "Runlin Wang"
date: "3/3/2024"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      message = FALSE, 
                      warning = FALSE,
                      comment = NA,
                      cache = TRUE)
```
# Load Packages 

```{r}
library(tidyverse)
library(tidytext)
library(pdftools)
library(tesseract)
library(furrr)
```
# Import Data, Extract Text Content, and Combine with Necessary Information to Create a Data Frame

## Read the .txt files containing course information

```{r}
course_name1 = read.table('course_name/course_name1.txt',header = T,sep = ',')
course_name2 = read.table('course_name/course_name2.txt',header = T,sep = ',')
```
## Create a data frame to store each syllabus' information and the text content in each PDF

```{r}
course_text = bind_rows(course_name1, course_name2) %>% 
  mutate(id = str_extract(x,'[[:digit:]]+ '),
         id = parse_number(id),
         x = str_remove(x,'[[:digit:]]+ '),
         split = str_split(x,'--'),
         department = map_chr(.x = split,
                              .f = ~unlist(.x)[1]),
         term = map_chr(.x = split,
                        .f = ~unlist(.x)[2]),
         course = map_chr(.x = split,
                          .f = ~unlist(.x)[3])) %>% 
  select(-x,-split) %>% 
  select(id,department,term,course) %>% 
  drop_na()
```
## Extract the text content of each PDF

```{r}
pdf_names = list.files('PDF')

extract_text_pdf = function(pdf_name){
  id_pdf = parse_number(pdf_name)
  text_pdf = pdf_ocr_text(pdf = str_c('PDF/',pdf_name))
  result = tibble(id = id_pdf, text = text_pdf)
  return(result)
}

plan(multisession, workers = 12)
pdf_text = future_map(.x = pdf_names,
                      .f = ~extract_text_pdf(pdf_name = .x),
                      .progress = TRUE)
```
## Merge text content from different pages in the same PDF

```{r}
pdf_text = do.call('rbind',pdf_text)
pdf_text = pdf_text %>% 
  group_by(id) %>% 
  summarise(content = str_c(text,collapse = ' ')) %>% 
  ungroup()
```
## Merge course information and text content

```{r}
course_text = course_text %>% 
  full_join(pdf_text,by = 'id')
```
# Output results

```{r}
write_csv(course_text,'course_text.csv')
```