---
title: "AI_in_Course_Syllabi"
subtitle: "analyze_text"
author: "Runlin Wang"
date: "3/3/2024"
output:
  html_document:
    fig_caption: yes
    number_sections: yes
    self_contained: yes
    theme: flatly
    toc: true
    toc_depth: 3
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      eval = TRUE,
                      message = FALSE, 
                      warning = FALSE,
                      comment = NA,
                      cache = TRUE)
```
# Load Packages

```{r}
library(tidyverse)
library(tidytext)
library(stopwords)
library(SnowballC)
library(wordcloud)
library(widyr)
library(ggforce)
library(igraph)
library(tidygraph)
library(ggraph)
```
# Import Data

## Read the organized data

```{r}
new_data = read_csv('new_data.csv')
```
# Data Preprocessing

## Read the data; replace "_" in text content with a space; tokenize the text content; delete the number words; delete the stop words; stem (an unknown step) 

```{r}
# add stop words related to course syllabi (uninformative words)
stopwords_user = tibble(word = c('student','class','exam','assignment','read',
                                 'write','week','time','ctp','ynp','http','https'), 
                        lexicon = 'user')
```
```{r}
token_data = new_data %>% 
  mutate(content = str_replace_all(content,'_',' ')) %>% 
  unnest_tokens(output = 'word',
                input = 'content',
                token = 'words') %>% 
  mutate(word = if_else(word=='al','ai',word)) %>% 
  filter(!str_detect(word,'[[:digit:]]+')) %>% 
  anti_join(bind_rows(stop_words,stopwords_user),by = 'word')
# %>% 
#   mutate(word = wordStem(word))
```
# Perform text analysis and visualize the findings

## Frequency count

```{r}
new_data %>% 
  count(label) %>% 
  drop_na() %>% 
  filter(label!='unknown') %>% 
  ggplot(aes(x = label,y = n,fill = label)) +
  geom_col() +
  labs(x = 'Attitude to AI',
       y = 'Frequency',
       title = 'Frequency of Attitudes to AI') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none')
```
## Proportional analysis by department

```{r}
new_data %>% 
  filter(label!='unknown') %>% 
  count(department,label) %>% 
  drop_na() %>% 
  ggplot(aes(x = department,y = n,fill = label)) +
  geom_bar(stat = 'identity',position = 'fill') +
  coord_flip() +
  labs(x = 'Proportion',
       y = 'Department',
       fill = 'Attitude to AI',
       title = 'Proportion of Attitude to AI by Departments') +
  theme_light()
```
## Top words in all PDFs

```{r}
token_data %>% 
  count(word) %>% 
  slice_max(order_by = n,n = 30) %>% 
  mutate(word = fct_reorder(word,n)) %>% 
  ggplot(aes(x = word,y = n)) +
  geom_col(fill = 'lightblue') +
  labs(x = 'Word',
       y = 'Frequency',
       title = 'Top words') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5))
```
## Top words by different labels

```{r}
token_data %>% 
  drop_na(label) %>% 
  count(label,word) %>% 
  group_by(label) %>% 
  slice_max(order_by = n,n = 10) %>% 
  mutate(word = reorder_within(x = word,by = n,within = label)) %>% 
  ggplot(aes(x = word,y = n,fill = label)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~label,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       title = 'Top words',
       fill = 'Attitude to AI') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5))
```
## Frequency of AI words

```{r}
ai_words = c('ai','al','gpt','chatgpt','generative','trained','transformer','artificial','intelligence','genai')
```
```{r}
token_data %>% 
  filter(word %in% ai_words) %>% 
  count(department) %>% 
  mutate(department = fct_reorder(department,n)) %>% 
  ggplot(aes(x = department,y = n)) +
  geom_col(fill = 'darkblue') +
  labs(x = 'Department',
       y = 'Frequency',
       title = 'Rank of department by frequency of using AI words') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 7))
```
## Frequency of AI words for "yes" label

```{r}
token_data %>% 
  filter(word %in% ai_words,
         label=='yes') %>% 
  count(department) %>% 
  mutate(department = fct_reorder(department,n)) %>% 
  ggplot(aes(x = department,y = n)) +
  geom_col(fill = 'darkgreen') +
  labs(x = 'Department',
       y = 'Frequency',
       subtitle = 'Attitude to AI: yes',
       title = 'Rank of department by frequency of using AI words') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 8))
```
## Frequency of AI words for "no" label

```{r}
token_data %>% 
  filter(word %in% ai_words,
         label=='no') %>% 
  count(department) %>% 
  mutate(department = fct_reorder(department,n)) %>% 
  ggplot(aes(x = department,y = n)) +
  geom_col(fill = 'darkred') +
  labs(x = 'Department',
       y = 'Frequency',
       subtitle = 'Attitude to AI: no',
       title = 'Rank of department by frequency of using AI words') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 8))
```
## Frequency of AI words for "neutral" label

```{r}
token_data %>% 
  filter(word %in% ai_words,
         label=='neutral') %>% 
  count(department) %>% 
  mutate(department = fct_reorder(department,n)) %>% 
  ggplot(aes(x = department,y = n)) +
  geom_col(fill = 'blue') +
  labs(x = 'Department',
       y = 'Frequency',
       subtitle = 'Attitude to AI: neutral',
       title = 'Rank of department by frequency of using AI words') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 8))
```
## Sentiment analysis using different lexicons

```{r}
bing_sentiment = get_sentiments('bing')
nrc_sentiment = get_sentiments('nrc')
afinn_sentiment = get_sentiments('afinn')
```
### Bing

```{r}
token_data %>% 
  inner_join(bing_sentiment,by = 'word') %>% 
  count(sentiment,word) %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n,n = 10) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(x = word,by = n,within = sentiment)) %>% 
  ggplot(aes(x = word,y = n,fill = sentiment)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~sentiment,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       title = 'Top words by sentiment') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none')
```
### Bing with different labels

```{r}
token_data %>% 
  filter(label=='yes') %>% 
  inner_join(bing_sentiment,by = 'word') %>% 
  count(sentiment,word) %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n,n = 10) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(x = word,by = n,within = sentiment)) %>% 
  ggplot(aes(x = word,y = n,fill = sentiment)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~sentiment,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       subtitle = 'Attitude to AI: yes',
       title = 'Top words by sentiment') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='no') %>% 
  inner_join(bing_sentiment,by = 'word') %>% 
  count(sentiment,word) %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n,n = 10) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(x = word,by = n,within = sentiment)) %>% 
  ggplot(aes(x = word,y = n,fill = sentiment)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~sentiment,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       subtitle = 'Attitude to AI: no',
       title = 'Top words by sentiment') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='neutral') %>% 
  inner_join(bing_sentiment,by = 'word') %>% 
  count(sentiment,word) %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n,n = 10) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(x = word,by = n,within = sentiment)) %>% 
  ggplot(aes(x = word,y = n,fill = sentiment)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~sentiment,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       subtitle = 'Attitude to AI: neutral',
       title = 'Top words by sentiment') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='unknown') %>% 
  inner_join(bing_sentiment,by = 'word') %>% 
  count(sentiment,word) %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n,n = 10) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(x = word,by = n,within = sentiment)) %>% 
  ggplot(aes(x = word,y = n,fill = sentiment)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~sentiment,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       subtitle = 'Attitude to AI: unknown',
       title = 'Top words by sentiment') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
### NRC

```{r}
token_data %>% 
  inner_join(nrc_sentiment,by = 'word') %>% 
  count(sentiment,word) %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n,n = 5) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(x = word,by = n,within = sentiment)) %>% 
  ggplot(aes(x = word,y = n,fill = sentiment)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~sentiment,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       title = 'Top words by sentiment') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        text = element_text(size = 8),
        legend.position = 'none')
```
### NRC with different labels

```{r}
token_data %>% 
  filter(label=='yes') %>% 
  inner_join(nrc_sentiment,by = 'word') %>% 
  count(sentiment,word) %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n,n = 5) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(x = word,by = n,within = sentiment)) %>% 
  ggplot(aes(x = word,y = n,fill = sentiment)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~sentiment,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       subtitle = 'Attitude to AI: yes',
       title = 'Top words by sentiment') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 8),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='no') %>% 
  inner_join(nrc_sentiment,by = 'word') %>% 
  count(sentiment,word) %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n,n = 5) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(x = word,by = n,within = sentiment)) %>% 
  ggplot(aes(x = word,y = n,fill = sentiment)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~sentiment,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       subtitle = 'Attitude to AI: no',
       title = 'Top words by sentiment') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 8),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='neutral') %>% 
  inner_join(nrc_sentiment,by = 'word') %>% 
  count(sentiment,word) %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n,n = 5) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(x = word,by = n,within = sentiment)) %>% 
  ggplot(aes(x = word,y = n,fill = sentiment)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~sentiment,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       subtitle = 'Attitude to AI: neutral',
       title = 'Top words by sentiment') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 8),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='unknown') %>% 
  inner_join(nrc_sentiment,by = 'word') %>% 
  count(sentiment,word) %>% 
  group_by(sentiment) %>% 
  slice_max(order_by = n,n = 5) %>% 
  ungroup() %>% 
  mutate(word = reorder_within(x = word,by = n,within = sentiment)) %>% 
  ggplot(aes(x = word,y = n,fill = sentiment)) +
  geom_col() +
  scale_x_reordered() +
  facet_wrap(~sentiment,scales = 'free') +
  labs(x = 'Word',
       y = 'Frequency',
       subtitle = 'Attitude to AI: unknown',
       title = 'Top words by sentiment') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 8),
        legend.position = 'none')
```
### AFINN

```{r}
token_data %>% 
  inner_join(afinn_sentiment,by = 'word') %>% 
  count(value) %>% 
  ggplot(aes(x = value,y = n,fill = value)) +
  geom_col() +
  labs(x = 'Score',
       y = 'Frequency',
       title = 'Sensiment Scores') +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = 'none')
```
### AFINN with different labels

```{r}
token_data %>% 
  filter(label=='yes') %>% 
  inner_join(afinn_sentiment,by = 'word') %>% 
  count(value) %>% 
  ggplot(aes(x = value,y = n,fill = value)) +
  geom_col() +
  labs(x = 'Score',
       y = 'Frequency',
       subtitle = 'Attitude to AI: yes',
       title = 'Sensiment Scores') +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='no') %>% 
  inner_join(afinn_sentiment,by = 'word') %>% 
  count(value) %>% 
  ggplot(aes(x = value,y = n,fill = value)) +
  geom_col() +
  labs(x = 'Score',
       y = 'Frequency',
       subtitle = 'Attitude to AI: no',
       title = 'Sensiment Scores') +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='neutral') %>% 
  inner_join(afinn_sentiment,by = 'word') %>% 
  count(value) %>% 
  ggplot(aes(x = value,y = n,fill = value)) +
  geom_col() +
  labs(x = 'Score',
       y = 'Frequency',
       subtitle = 'Attitude to AI: neutral',
       title = 'Sensiment Scores') +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='unknown') %>% 
  inner_join(afinn_sentiment,by = 'word') %>% 
  count(value) %>% 
  ggplot(aes(x = value,y = n,fill = value)) +
  geom_col() +
  labs(x = 'Score',
       y = 'Frequency',
       subtitle = 'Attitude to AI: unknown',
       title = 'Sensiment Scores') +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
### Sentiment proportion (BING)

```{r}
token_data %>% 
  inner_join(bing_sentiment,by = 'word') %>% 
  count(department,sentiment) %>% 
  ggplot(aes(x = department,y = n,fill = sentiment)) +
  geom_bar(stat = 'identity',position = 'fill') +
  labs(x = 'Department',
       y = 'Proportion',
       fill = 'Sentiment',
       title = 'Sentiment by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        text = element_text(size = 7))
```
### Sentiment proportion (BING) with different labels

```{r}
token_data %>% 
  filter(label=='yes') %>% 
  inner_join(bing_sentiment,by = 'word') %>% 
  count(department,sentiment) %>% 
  ggplot(aes(x = department,y = n,fill = sentiment)) +
  geom_bar(stat = 'identity',position = 'fill') +
  labs(x = 'Department',
       y = 'Proportion',
       fill = 'Sentiment',
       subtitle = 'Attitude to AI: yes',
       title = 'Sentiment by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        text = element_text(size = 10))
```
```{r}
token_data %>% 
  filter(label=='no') %>% 
  inner_join(bing_sentiment,by = 'word') %>% 
  count(department,sentiment) %>% 
  ggplot(aes(x = department,y = n,fill = sentiment)) +
  geom_bar(stat = 'identity',position = 'fill') +
  labs(x = 'Department',
       y = 'Proportion',
       fill = 'Sentiment',
       subtitle = 'Attitude to AI: no',
       title = 'Sentiment by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        text = element_text(size = 10))
```
```{r}
token_data %>% 
  filter(label=='neutral') %>% 
  inner_join(bing_sentiment,by = 'word') %>% 
  count(department,sentiment) %>% 
  ggplot(aes(x = department,y = n,fill = sentiment)) +
  geom_bar(stat = 'identity',position = 'fill') +
  labs(x = 'Department',
       y = 'Proportion',
       fill = 'Sentiment',
       subtitle = 'Attitude to AI: neutral',
       title = 'Sentiment by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        text = element_text(size = 10))
```
```{r}
token_data %>% 
  filter(label=='unknown') %>% 
  inner_join(bing_sentiment,by = 'word') %>% 
  count(department,sentiment) %>% 
  ggplot(aes(x = department,y = n,fill = sentiment)) +
  geom_bar(stat = 'identity',position = 'fill') +
  labs(x = 'Department',
       y = 'Proportion',
       fill = 'Sentiment',
       subtitle = 'Attitude to AI: unknown',
       title = 'Sentiment by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        text = element_text(size = 7))
```
### Sentiment proportion (NRC)

```{r}
token_data %>% 
  inner_join(nrc_sentiment,by = 'word') %>% 
  count(department,sentiment) %>% 
  ggplot(aes(x = department,y = n,fill = sentiment)) +
  geom_bar(stat = 'identity',position = 'fill') +
  labs(x = 'Department',
       y = 'Proportion',
       fill = 'Sentiment',
       title = 'Sentiment by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        text = element_text(size = 7))
```
### Sentiment proportion (NRC) with different labels

```{r}
token_data %>% 
  filter(label=='yes') %>% 
  inner_join(nrc_sentiment,by = 'word') %>% 
  count(department,sentiment) %>% 
  ggplot(aes(x = department,y = n,fill = sentiment)) +
  geom_bar(stat = 'identity',position = 'fill') +
  labs(x = 'Department',
       y = 'Proportion',
       fill = 'Sentiment',
       subtitle = 'Attitude to AI: yes',
       title = 'Sentiment by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        text = element_text(size = 10))
```
```{r}
token_data %>% 
  filter(label=='no') %>% 
  inner_join(nrc_sentiment,by = 'word') %>% 
  count(department,sentiment) %>% 
  ggplot(aes(x = department,y = n,fill = sentiment)) +
  geom_bar(stat = 'identity',position = 'fill') +
  labs(x = 'Department',
       y = 'Proportion',
       fill = 'Sentiment',
       subtitle = 'Attitude to AI: no',
       title = 'Sentiment by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        text = element_text(size = 10))
```
```{r}
token_data %>% 
  filter(label=='neutral') %>% 
  inner_join(nrc_sentiment,by = 'word') %>% 
  count(department,sentiment) %>% 
  ggplot(aes(x = department,y = n,fill = sentiment)) +
  geom_bar(stat = 'identity',position = 'fill') +
  labs(x = 'Department',
       y = 'Proportion',
       fill = 'Sentiment',
       subtitle = 'Attitude to AI: neutral',
       title = 'Sentiment by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        text = element_text(size = 10))
```
```{r}
token_data %>% 
  filter(label=='unknown') %>% 
  inner_join(nrc_sentiment,by = 'word') %>% 
  count(department,sentiment) %>% 
  ggplot(aes(x = department,y = n,fill = sentiment)) +
  geom_bar(stat = 'identity',position = 'fill') +
  labs(x = 'Department',
       y = 'Proportion',
       fill = 'Sentiment',
       subtitle = 'Attitude to AI: unknown',
       title = 'Sentiment by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        text = element_text(size = 7))
```
### Sentiment score (AFINN)

```{r}
token_data %>% 
  inner_join(afinn_sentiment,by = 'word') %>% 
  group_by(department) %>% 
  summarise(score = mean(value)) %>% 
  ungroup() %>% 
  mutate(department = fct_reorder(department,score)) %>% 
  ggplot(aes(x = department,y = score,fill = score)) +
  geom_col() +
  labs(x = 'Department',
       y = 'Sentiment Score',
       title = 'Sentiment Score by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        text = element_text(size = 7),
        legend.position = 'none')
```
### Sentiment score (AFINN) by different labels

```{r}
token_data %>% 
  filter(label=='yes') %>% 
  inner_join(afinn_sentiment,by = 'word') %>% 
  group_by(department) %>% 
  summarise(score = mean(value)) %>% 
  ungroup() %>% 
  mutate(department = fct_reorder(department,score)) %>% 
  ggplot(aes(x = department,y = score,fill = score)) +
  geom_col() +
  labs(x = 'Department',
       y = 'Sentiment Score',
       subtitle = 'Attitude to AI: yes',
       title = 'Sentiment Score by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='no') %>% 
  inner_join(afinn_sentiment,by = 'word') %>% 
  group_by(department) %>% 
  summarise(score = mean(value)) %>% 
  ungroup() %>% 
  mutate(department = fct_reorder(department,score)) %>% 
  ggplot(aes(x = department,y = score,fill = score)) +
  geom_col() +
  labs(x = 'Department',
       y = 'Sentiment Score',
       subtitle = 'Attitude to AI: no',
       title = 'Sentiment Score by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='neutral') %>% 
  inner_join(afinn_sentiment,by = 'word') %>% 
  group_by(department) %>% 
  summarise(score = mean(value)) %>% 
  ungroup() %>% 
  mutate(department = fct_reorder(department,score)) %>% 
  ggplot(aes(x = department,y = score,fill = score)) +
  geom_col() +
  labs(x = 'Department',
       y = 'Sentiment Score',
       subtitle = 'Attitude to AI: neutral',
       title = 'Sentiment Score by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        legend.position = 'none')
```
```{r}
token_data %>% 
  filter(label=='unknown') %>% 
  inner_join(afinn_sentiment,by = 'word') %>% 
  group_by(department) %>% 
  summarise(score = mean(value)) %>% 
  ungroup() %>% 
  mutate(department = fct_reorder(department,score)) %>% 
  ggplot(aes(x = department,y = score,fill = score)) +
  geom_col() +
  labs(x = 'Department',
       y = 'Sentiment Score',
       subtitle = 'Attitude to AI: unknown',
       title = 'Sentiment Score by Department') +
  coord_flip() +
  theme_light() +
  theme(plot.title = element_text(hjust = 0.5),
        plot.subtitle = element_text(hjust = 0.5),
        axis.text.y = element_text(size = 6),
        legend.position = 'none')
```
## Word clouds

```{r}
token_data %>%
  inner_join(bing_sentiment,by = 'word') %>%
  count(word, sentiment, sort = TRUE) %>%
  pivot_wider(names_from = 'sentiment',
              values_from = 'n',
              values_fill = 0) %>% 
  as.data.frame() %>% 
  column_to_rownames(var = 'word') %>% 
  comparison.cloud(colors = c("red", "blue"),
                   max.words = 80)
```
## Word clouds by different labels

```{r}
token_data %>%
  filter(label=='yes') %>% 
  inner_join(bing_sentiment,by = 'word') %>%
  count(word, sentiment, sort = TRUE) %>%
  pivot_wider(names_from = 'sentiment',
              values_from = 'n',
              values_fill = 0) %>% 
  as.data.frame() %>% 
  column_to_rownames(var = 'word') %>% 
  comparison.cloud(colors = c("blue", "red"),
                   max.words = 80)
```
```{r}
token_data %>%
  filter(label=='no') %>% 
  inner_join(bing_sentiment,by = 'word') %>%
  count(word, sentiment, sort = TRUE) %>%
  pivot_wider(names_from = 'sentiment',
              values_from = 'n',
              values_fill = 0) %>% 
  as.data.frame() %>% 
  column_to_rownames(var = 'word') %>% 
  comparison.cloud(colors = c("red", "blue"),
                   max.words = 80)
```
```{r}
token_data %>%
  filter(label=='neutral') %>% 
  inner_join(bing_sentiment,by = 'word') %>%
  count(word, sentiment, sort = TRUE) %>%
  pivot_wider(names_from = 'sentiment',
              values_from = 'n',
              values_fill = 0) %>% 
  as.data.frame() %>% 
  column_to_rownames(var = 'word') %>% 
  comparison.cloud(colors = c("blue", "red"),
                   max.words = 80)
```
```{r}
token_data %>%
  filter(label=='unknown') %>% 
  inner_join(bing_sentiment,by = 'word') %>%
  count(word, sentiment, sort = TRUE) %>%
  pivot_wider(names_from = 'sentiment',
              values_from = 'n',
              values_fill = 0) %>% 
  as.data.frame() %>% 
  column_to_rownames(var = 'word') %>% 
  comparison.cloud(colors = c("blue", "red"),
                   max.words = 80)
```
## Network diagrams

### Count pairs of words within PDFs

```{r}
word_cooccurences_pdf = pairwise_count(tbl = token_data,
                                       item = 'word',
                                       feature = 'id',
                                       sort = T)
```
### Co-occurence of words within PDFs

```{r}
set.seed(1)
word_cooccurences_pdf %>%
  filter(item1 %in% ai_words | item2 %in% ai_words) %>% 
  top_n(1000) %>%
  graph_from_data_frame() %>%
  ggraph(layout = 'fr') +
  geom_edge_link(aes(edge_alpha = n,edge_width = n)) +
  geom_node_point(color = 'lightblue',size = 3) +
  geom_node_text(aes(label = name),vjust = 1.8,col = 'blue') +
  labs(title = 'Co-Occurrence of Words') +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5))
```
### Find correlations of words within PDFs

```{r}
word_correlations_pdf = token_data %>%
  add_count(word) %>%
  filter(n>100) %>%
  select(-n) %>%
  pairwise_cor(item = word,
               feature = id,
               sort = T)
```
```{r}
set.seed(1)
word_correlations_pdf %>%
  filter(item1 %in% ai_words | item2 %in% ai_words) %>% 
  filter(correlation > 0.22) %>%
  as_tbl_graph() %>%
  ggraph(layout = 'fr') +
  geom_edge_link(aes(edge_alpha = correlation),show.legend = F) +
  geom_node_point(color = 'lightblue',size = 2) +
  geom_node_text(aes(label = name), repel = T) +
  labs(title = 'Correlation of Words') +
  theme_void() +
  theme(plot.title = element_text(hjust = 0.5))
```